### 2018-10-16 tex/evaluation.tex
Verision 2.3

The second shuffle of Terasort partitions the data through a Spark RangePartitioner. 
% As the range bounds set by range partitioner almost match the same pattern of the first shuffle, almost $93\%$ of input data is from one particular map task for each reduce task. So we take the second shuffle as an extreme case to evaluate the scheduling locality for SCache.
In the second shuffle, almost $93\%$ of input data of a reduce task is produced by one particular map task. 
So we take the second shuffle as an extreme case to evaluate the heuristic locality swap of SCache.
In this shuffle, Spark schedules a reduce task to the node that produces most input data. 
By doing this, Spark minimizes the shuffle data through network. 
At the same time, Figure \ref{fig:terashuffle} reveals that SCache produces exactly same network traffic as Spark. 
It implies that the heuristic locality swap of SCache can obtain the best locality while balancing the load.

\begin{figure*}
	\centering
	\includegraphics[width=0.85\textwidth]{fig/tpcds}
	\caption{TPC-DS Benchmark Evaluation}
	\label{fig:tpcds}
	\vspace{-1em}
\end{figure*}
\begin{figure}
	\centering
	\includegraphics[width=0.6\linewidth]{fig/sampling}
	\caption{Sampling Overhead}
	\label{fig:sampling}
	\vspace{-1em}
\end{figure}

@@

To prove SCache compatibility as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce as the external shuffle service and co-scheduler. Although \textit{pre-scheduling reduce tasks} is not critical for the simple DAG computing in Hadoop MapReduce, some shuffle-heavy jobs on Hadoop Madpreduce can still be optimized by SCache shuffle data management.

Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop MapReduce running Terasort. Both figures have the same proportion of time. Hadoop MapReduce with SCache brings 15\% of total time optimization with 384GB input data size. 
As shown in the Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache writes intermediate data locally in the map phase. The shuffle phase and reduce phase start simultaneously. Because the large amount of shuffle data reaches the network bottleneck, the beginning part of reduce needs to wait needs to wait for network transfer. This causes the CPU resources to be idle. 
As shown in the Figure \ref{fig:hadoop_terasort_scache}, Hadoop Madpreduce with SCache start pre-fetching in the map phase. This avoids the reduce phase waiting for the shuffle data. Furthermore, pre-fetching utilizes the idle IO throughput in the map phase. As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop MapReduce with SCache optimize Terasort overall completion time by up to 15\% and an average of 13\% with input data sizes from 128GB to 512GB.
}

\begin{figure}
	\centering
	\begin{minipage}[hb]{\linewidth}
		\begin{subfigure}{\linewidth}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/hadoop_terasort_scache}
				\caption{\color{blue}Hadoop MapReduce With SCache}
				\label{fig:hadoop_terasort_scache}
			\end{minipage}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/hadoop_terasort_origin}
				\caption{\color{blue}Hadoop MapReduce Without SCache}
				\label{fig:hadoop_terasort_origin}
			\end{minipage}
		\end{subfigure}
		\caption{\color{blue}CPU utilization and I/O throughput of a node during a Hadoop MapReduce Terasort job}
		\label{fig:hadoop_terasort}
	\end{minipage}
\end{figure}

\begin{figure}
	\includegraphics[width=\linewidth]{fig/hadoop_terasort_time}
	\caption{\color{blue}Hadoop MapReduce Terasort completion time}
	\label{fig:hadoop_terasort_time}
\end{figure}

>>>>

The second shuffle of Terasort partitions the data through a Spark RangePartitioner. 
% As the range bounds set by range partitioner almost match the same pattern of the first shuffle, almost $93\%$ of input data is from one particular map task for each reduce task. So we take the second shuffle as an extreme case to evaluate the scheduling locality for SCache.
In the second shuffle, almost $93\%$ of input data of a reduce task is produced by one particular map task. 
So we take the second shuffle as an extreme case to evaluate the heuristic locality swap of SCache.
In this shuffle, Spark schedules a reduce task to the node that produces most input data. 
By doing this, Spark minimizes the shuffle data through network. 
At the same time, Figure \ref{fig:terashuffle} reveals that SCache produces exactly same network traffic as Spark. 
It implies that the heuristic locality swap of SCache can obtain the best locality while balancing the load. 
\begin{figure}
	\centering
	\begin{minipage}[hb]{\linewidth}
		\begin{subfigure}{\linewidth}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/hadoop_terasort_scache}
				\caption{\color{blue}Hadoop MapReduce With SCache}
				\label{fig:hadoop_terasort_scache}
			\end{minipage}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/hadoop_terasort_origin}
				\caption{\color{blue}Hadoop MapReduce Without SCache}
				\label{fig:hadoop_terasort_origin}
			\end{minipage}
		\end{subfigure}
		\caption{\color{blue}CPU utilization and I/O throughput of a node during a Hadoop MapReduce Terasort job}
		\label{fig:hadoop_terasort}
	\end{minipage}
\end{figure}
\begin{figure*}
	\centering
	\includegraphics[width=0.85\textwidth]{fig/tpcds}
	\caption{TPC-DS Benchmark Evaluation}
	\label{fig:tpcds}
	\vspace{-1em}
\end{figure*}
\begin{figure}
	\includegraphics[width=\linewidth]{fig/hadoop_terasort_time}
	\caption{\color{blue}Hadoop MapReduce Terasort completion time}
	\label{fig:hadoop_terasort_time}
\end{figure}

@@

To prove SCache compatibility as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce as the external shuffle service and co-scheduler. Although \textit{pre-scheduling reduce tasks} is not critical for the simple DAG computing such as Hadoop MapReduce, some shuffle-heavy jobs on Hadoop MapReduce can still be optimized by SCache shuffle data management.

Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop MapReduce running Terasort. Both figures have the same proportion of time. Hadoop MapReduce with SCache brings 15\% of total time optimization with 384GB input data size. 
As shown in Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache writes intermediate data locally in the map phase. The shuffle phase and reduce phase start simultaneously. Because a large amount of shuffle data reaches the network bottleneck, the beginning part of reduce needs to wait for network transfer. This causes the CPU resources to be idle. 
As shown in Figure \ref{fig:hadoop_terasort_scache}, Hadoop MapReduce with SCache start pre-fetching in the map phase. This avoids the reduce phase waiting for the shuffle data. Furthermore, pre-fetching utilizes the idle IO throughput in the map phase. As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop MapReduce with SCache optimize Terasort overall completion time by up to 15\% and an average of 13\% with input data sizes from 128GB to 512GB.
}

\begin{figure}
	\centering
	\includegraphics[width=0.6\linewidth]{fig/sampling}
	\caption{Sampling Overhead}
	\label{fig:sampling}
	\vspace{-1em}
\end{figure}

### 2018-10-16 tex/impl.tex
Verision 2.3

\section{Implementation}\label{impl}
This section presents an overview of the implementation of SCache. 
% {\color{red}
% Here we use Spark as an example of DAG framework to illustrate the work flow of shuffle optimization. 
% We will first present the system overview in Subsection \ref{arch} while the following two subsections focus on the two constraints on memory management.
% }
{\color{blue}
We first present the system overview and the detail of sampling in Subsection \ref{arch}. 
The following \ref{memorymanage} subsection focuses on the two constraints on memory management.
In Subsection \ref{crossframework}, we will evaluate cross-framework capability of SCache based on Hadoop MapReduce and Spark. 
At last, we discuss the cost of adapting SCache and the fault tolerance. 
}

\subsection{System Overview}\label{arch}
SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a %{\color{red}daemon inside Spark.}
{\color{blue} worker daemon. As a plug-in system, SCache needs to rely on a DAG framework.} As shown in Figure \ref{fig:architecture}, SCache employs the legacy master-slaves architecture like GFS \cite{gfs} for shuffle data management system. 
The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
The coordination provides two guarantees: (a)data is stored in memory before tasks start and (b)data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
The daemon bridges the communication between %{\color{red}Spark}
{\color{blue} DAG framework} and SCache. The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to %{\color{red}Spark scheduler}
 {\color{blue} original scheduler in framework}.

@@

When a map task finishes computing, the shuffle write implementation of DAG framework is modified to call the SCache API and move all the blocks out of {\color{blue}framework worker} through memory copy. 
After that the slot will be released (without being blocked on disk operations).
When a block of the map output (i.e., "map output" in Figure \ref{fig:shuffle}) is received, the SCache worker will send the block ID and the size to the master.
If the collected map output data reach the observation threshold, the DAG co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks and then broadcast the scheduling result to start pre-fetching on each worker.
% After that, when a map task is finished, each node will receive a broadcast message. 
SCache worker will filter the reduce tasks' IDs that are scheduled on itself and start pre-fetching shuffle data from the remote. 
% {\color{red}
% To enforce SCache pre-scheduled tasks -- node mapping, we insert some lines of codes in Spark DAG Scheduler.
% For RDDs with shuffle dependencies, Spark DAG scheduler will consult SCache master to get the preferred location for each partition and set \textit{NODE\_LOCAL} locality level on corresponding reduce tasks.
% }
{\color{blue}
In order to force DAG framework to run according to the SCache pre-scheduled results, we insert some lines of codes in framework scheduler.
After modification, DAG scheduler will consult SCache co-scheduler to get the preferred location for each task.
}
% In the case of extreme skew scenario, such as Figure \ref{fig:range_pre_sample}, Heuristic MinHeap trades about 0.05\% percent of stage completion time for 99\% reduction of shuffle data transmission through network by heuristicly swapping tasks.
% \begin{minipage}{\columnwidth}
% \begin{algorithm}[H]
% \caption{Accumulate Heuristic Scheduling for Multi-Shuffles}
% \label{mhminheap}
% 	\begin{algorithmic}[1]
% 	\small
% 	\Procedure{\Large m\_schedule}{$m, host\_id, p\_reduces, shuffles$}
% 		\State $m\gets$ partition number of map tasks
% 		\Comment $shuffles$ is the previous schedule result 
% 		\ForAll{$r$ in $p\_reduces$}
% 			\State $r.size \mathrel{+}= shuffles\left[r.rid\right].size$
% 			\If{$shuffles\left[r.rid\right].size\geq r.size \times r.prob$}
% 				\State $r.prob\gets shuffles\left[r.rid\right].size / r.size$
% 				\State $r.host\_id\gets shuffles\left[r.rid\right].assigned\_host$
% 			\EndIf
% 		\EndFor
% 		\State $M\gets$ $SCHEDULE\left(m, host\_id, p\_reduces\right)$
% 		\ForAll{$host\_id$ in $M$}
% 			\Comment Re-shuffle
% 			\ForAll{$r$ in $M\left[host\_id\right].reduces$}
% 				\If{$host\neq shuffles\left[r.rid\right].assigned\_host$}
% 				\State Re-shuffle data to $host$
% 				\State $shuffles\left[r.rid\right].assigned\_host\gets host$
% 				\EndIf
% 			\EndFor
% 		\EndFor
% 		\Return $M$
% 	\EndProcedure
% 	\end{algorithmic}
% \end{algorithm}
% \end{minipage}

@@

% {\color{red}
% \subsection{Cost of adapting DAG frameworks}
% SCache provides API through RPC, such as \textit{putBlock(blockId)}, \textit{getBlock(blockId)}, and \textit{getScheduleResult(shuffleId)}. The concise design makes it easy to adapt DAG frameworks to enable SCache optimization. For example, it only takes about 500 lines of code in Spark to integrate SCache. By a glance of Hadoop source code, we believe that the costs of enabling SCache on MapReduce \cite{hadoop} and YARN \cite{yarn} based DAG computing framework, such as Tez \cite{tez}, are also very low.
% }
{\color{blue}
\subsection{Analysis of cross-framework capability}\label{crossframework}
Shuffle optimization of SCache inevitably requires modification on dependent DAG framework. SCache provides API through RPC, such as \textit{putBlock (blockId)}, \textit{getBlock (blockId)}, and \textit{getScheduleResult (shuffleId)}. In order to use SCache, we mainly need to modify the two parts of the framework: (a)We need to insert codes in the DAG scheduler to let framework provide DAG information and follow pre-scheduled result of SCache. (b)The shuffle data between the Map task and the Reduce task should be transfered to SCahce Storge Management.

>>>>

\section{Implementation}\label{impl}
This section presents an overview of the implementation of SCache. 
% {\color{red}
% Here we use Spark as an example of DAG framework to illustrate the work flow of shuffle optimization. 
% We will first present the system overview in Subsection \ref{arch} while the following two subsections focus on the two constraints on memory management.
% }
{\color{blue}
We first present the system overview and the detail of sampling in Subsection \ref{arch}. 
The following \ref{memorymanage} subsection focuses on the two constraints on memory management.
In Subsection \ref{crossframework}, we will evaluate cross-framework capability of SCache based on Hadoop MapReduce and Spark. 
At last, we discuss the cost of adapting SCache and fault tolerance. 
}

\subsection{System Overview}\label{arch}
SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a %{\color{red}daemon inside Spark.}
{\color{blue} worker daemon. As a plug-in system, SCache needs to rely on a DAG framework.} As shown in Figure \ref{fig:architecture}, SCache employs the legacy master-slaves architecture like GFS \cite{gfs} for the shuffle data management system. 
The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
The coordination provides two guarantees: (a)data is stored in memory before tasks start and (b)data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
The daemon bridges the communication between %{\color{red}Spark}
{\color{blue} DAG framework} and SCache. The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to %{\color{red}Spark scheduler}
 {\color{blue} original scheduler in framework}.

@@

When a map task finishes computing, the shuffle write implementation of DAG framework is modified to call the SCache API and move all the blocks out of {\color{blue}framework worker} through memory copy. 
After that, the slot will be released (without being blocked on disk operations).
When a block of the map output (i.e., "map output" in Figure \ref{fig:shuffle}) is received, the SCache worker will send the block ID and the size to the master.
If the collected map output data reach the observation threshold, the DAG co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks and then broadcast the scheduling result to start pre-fetching on each worker.
% After that, when a map task is finished, each node will receive a broadcast message. 
SCache worker will filter the reduce tasks' IDs that are scheduled on itself and start pre-fetching shuffle data from the remote. 
% {\color{red}
% To enforce SCache pre-scheduled tasks -- node mapping, we insert some lines of codes in Spark DAG Scheduler.
% For RDDs with shuffle dependencies, Spark DAG scheduler will consult SCache master to get the preferred location for each partition and set \textit{NODE\_LOCAL} locality level on corresponding reduce tasks.
% }
{\color{blue}
In order to force DAG framework to run according to the SCache pre-scheduled results, we insert some lines of codes in framework scheduler.
After modification, DAG scheduler will consult SCache co-scheduler to get the preferred location for each task.
}
% In the case of extreme skew scenario, such as Figure \ref{fig:range_pre_sample}, Heuristic MinHeap trades about 0.05\% percent of stage completion time for 99\% reduction of shuffle data transmission through network by heuristicly swapping tasks.
% \begin{minipage}{\columnwidth}
% \begin{algorithm}[H]
% \caption{Accumulate Heuristic Scheduling for Multi-Shuffles}
% \label{mhminheap}
% 	\begin{algorithmic}[1]
% 	\small
% 	\Procedure{\Large m\_schedule}{$m, host\_id, p\_reduces, shuffles$}
% 		\State $m\gets$ partition number of map tasks
% 		\Comment $shuffles$ is the previous schedule result 
% 		\ForAll{$r$ in $p\_reduces$}
% 			\State $r.size \mathrel{+}= shuffles\left[r.rid\right].size$
% 			\If{$shuffles\left[r.rid\right].size\geq r.size \times r.prob$}
% 				\State $r.prob\gets shuffles\left[r.rid\right].size / r.size$
% 				\State $r.host\_id\gets shuffles\left[r.rid\right].assigned\_host$
% 			\EndIf
% 		\EndFor
% 		\State $M\gets$ $SCHEDULE\left(m, host\_id, p\_reduces\right)$
% 		\ForAll{$host\_id$ in $M$}
% 			\Comment Re-shuffle
% 			\ForAll{$r$ in $M\left[host\_id\right].reduces$}
% 				\If{$host\neq shuffles\left[r.rid\right].assigned\_host$}
% 				\State Re-shuffle data to $host$
% 				\State $shuffles\left[r.rid\right].assigned\_host\gets host$
% 				\EndIf
% 			\EndFor
% 		\EndFor
% 		\Return $M$
% 	\EndProcedure
% 	\end{algorithmic}
% \end{algorithm}
% \end{minipage}

@@

% {\color{red}
% \subsection{Cost of adapting DAG frameworks}
% SCache provides API through RPC, such as \textit{putBlock(blockId)}, \textit{getBlock(blockId)}, and \textit{getScheduleResult(shuffleId)}. The concise design makes it easy to adapt DAG frameworks to enable SCache optimization. For example, it only takes about 500 lines of code in Spark to integrate SCache. By a glance of Hadoop source code, we believe that the costs of enabling SCache on MapReduce \cite{hadoop} and YARN \cite{yarn} based DAG computing framework, such as Tez \cite{tez}, are also very low.
% }
{\color{blue}
\subsection{Analysis of cross-framework capability}\label{crossframework}
Shuffle optimization of SCache inevitably requires modification on dependent DAG framework. SCache provides API through RPC, such as \textit{putBlock (blockId)}, \textit{getBlock (blockId)}, and \textit{getScheduleResult (shuffleId)}. In order to use SCache, we mainly need to modify the two parts of the framework: (a)We need to insert codes in the DAG scheduler to let framework provide DAG information and follow the pre-scheduled result of SCache. (b)The shuffle data between the Map task and the Reduce task should be transferred to SCahce Storge Management.

### 2018-10-16 tex/intro.tex
Verision 2.3

Although continuous efforts of performance optimization have been made among a variety of computing frameworks \cite{sync, babu, tachyon, pacman, quincy, delay}, 
the shuffle is often poorly optimized in practice.
% take over shuffle
%shuffle characteristic
In particular, we observe that one major deficiency lies in the lack of fine-grained, coordinated management among different system resources.
%In the current practice, the shuffle phase is often split into two parts --- \textit{shuffle read} and \textit{shuffle write}. 
As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stages (i.e., map task).  
And the \textit{shuffle read} fetches intermediate results from remote disks through network, which is commonly integrated as part of the tasks in descendant stages (i.e., reduce task). 
Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk and network) named \textit{slot} is assigned to a task, and the resources are released only after the task finishes.
Such task aggregation together with the coarse-grained scheduling effectively simplifies task management.
However, since a cluster has a limited number of slots, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
%The map task in Figure \ref{fig:workflow} well explains such deficiency: the I/O resource allocated to the stage is always idle during the computation time, and the computation/memory resource is totally wasted during the shuffle write attached to it, and vice versa.
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fig/workflow}
	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
	\label{fig:workflow}
\end{figure}

Moreover, the shuffle read phase introduces all-to-all communication pattern across the network, and such network I/O procedure is also poorly coordinated.
Note that the shuffle read phase starts fetching data only after the corresponding reduce task starts.
Meanwhile, the reduce tasks belonging to a same execution phase are scheduled at the same time by default. 
As a result, all the corresponding reduce tasks start fetching shuffle data almost simultaneously.
Such synchronized network communication causes a burst demand for network I/O, which in turn greatly enlarges the shuffle read completion time. 
To desynchronize the network communication, an intuitive way is to launch some tasks in the descendent stage earlier, such as "slow-start" from Hadoop MapReduce\footnote{http://hadoop.apache.com/}. 
However, such early-start is by no means a panacea. 
This is because the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.

@@

{\color{blue}
In order to visually analyze above-mentioned resources scheduling, we propose a performance model called \textit{Framework Resources Quantification} (FRQ) model. FRQ model quantifies computing and I/O resources and displays resources scheduling strategy of DAG framework in time dimension. We use FRQ model to assist in analyze the deficiencies of resources scheduling and optimize it. 
FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
According to the above five parameters and the scheduling strategy of the DAG framework, FRQ model is able to calculate the execution time of each phase of a computing job. 
Take Apache Hadoop MapReduce as a simple DAG computing example, we use FRQ to model each phases of the computing, including Map, Shuffle, and Reduce.
By revealing the relationships between the various phases, FRQ model assist us in discovering the irrationality of resource scheduling during computing.
I/O resource in map phase is not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
This situation will be amplified in shuffle-heavy tasks.
}

@@

{\color{blue}
We have implemented SCache, a customized Apache Spark \cite{apachespark} and a customized Apache Hadoop. We have also designed a performance model called \textit{Framework Resources Quantification} (FRQ) model to analyze the shuffle optimization of SCache and calculate the execution time of each phase of computing job. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop. On Apache Spark, we conduct basic test \textit{GroupByTest}. We also evaluate Terasort\footnote{https://github.com/ehiggs/spark-terasort} benchmark and standard workloads like TPC-DS\footnote{http://www.tpc.org/tpcds/} for multi-tenant modeling. On Apache Hadoop, we focus on Terasort benchmark. In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied applications. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average on Apache Spark. On Apache Hadoop, SCache optimize end-to-end Terasort completion time by 15\%.
}

>>>>

Although continuous efforts of performance optimization have been made among a variety of computing frameworks \cite{sync, babu, tachyon, pacman, quincy, delay}, 
the shuffle is often poorly optimized in practice.
% take over shuffle
%shuffle characteristic
In particular, we observe that one major deficiency lies in the lack of fine-grained, coordinated management among different system resources.
%In the current practice, the shuffle phase is often split into two parts --- \textit{shuffle read} and \textit{shuffle write}. 
As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stages (i.e., map task).  
And the \textit{shuffle read} fetches intermediate results from remote disks through network, which is commonly integrated as part of the tasks in descendant stages (i.e., reduce task). 
Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk, and network) named \textit{slot} is assigned to a task, and the resources are released only after the task finishes.
Such task aggregation together with the coarse-grained scheduling effectively simplifies task management.
However, since a cluster has a limited number of slots, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
%The map task in Figure \ref{fig:workflow} well explains such deficiency: the I/O resource allocated to the stage is always idle during the computation time, and the computation/memory resource is totally wasted during the shuffle write attached to it, and vice versa.
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fig/workflow}
	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
	\label{fig:workflow}
\end{figure}

Moreover, the shuffle read phase introduces all-to-all communication pattern across the network, and such network I/O procedure is also poorly coordinated.
Note that the shuffle read phase starts fetching data only after the corresponding reduce task starts.
Meanwhile, the reduce tasks belonging to the same execution phase are scheduled at the same time by default. 
As a result, all the corresponding reduce tasks start fetching shuffle data almost simultaneously.
Such synchronized network communication causes a burst demand for network I/O, which in turn greatly enlarges the shuffle read completion time. 
To desynchronize the network communication, an intuitive way is to launch some tasks in the descendent stage earlier, such as "slow-start" from Hadoop MapReduce\footnote{http://hadoop.apache.com/}. 
However, such early-start is by no means a panacea. 
This is because the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.

@@

{\color{blue}
In order to visually analyze above-mentioned resources scheduling, we propose a performance model called \textit{Framework Resources Quantification} (FRQ) model. FRQ model quantifies computing and I/O resources and displays resources scheduling strategy of DAG framework in the time dimension. We use FRQ model to assist in analyze the deficiencies of resources scheduling and optimize it. 
FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
According to the above five parameters and the scheduling strategy of the DAG framework, FRQ model is able to calculate the execution time of each phase of a computing job. 
Take Apache Hadoop MapReduce as a simple DAG computing example, we use FRQ to model each phase of the computing, including Map, Shuffle, and Reduce.
By revealing the relationships between the various phases, FRQ model assists us in discovering the irrationality of resource scheduling during computing.
I/O resource in map phase is not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
This situation will be amplified in shuffle-heavy tasks.
}

@@

{\color{blue}
We have implemented SCache, a customized Apache Spark \cite{apachespark} and a customized Apache Hadoop. We have also designed a performance model called \textit{Framework Resources Quantification} (FRQ) model to analyze the shuffle optimization of SCache and calculate the execution time of each phase of a computing job. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop. On Apache Spark, we conduct basic test \textit{GroupByTest}. We also evaluate Terasort\footnote{https://github.com/ehiggs/spark-terasort} benchmark and standard workloads like TPC-DS\footnote{http://www.tpc.org/tpcds/} for multi-tenant modeling. On Apache Hadoop, we focus on Terasort benchmark. In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied applications. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average on Apache Spark. On Apache Hadoop, SCache optimizes end-to-end Terasort completion time by 15\%.
}
